SubsidyExplorer - Step 7: Pre-Populated Proposals

### 2021-10-22 scripts/07_proposals.Rmd
prep for rehost and DOI

@@

write.csv(all_results_regional_output_table_2050_pretty, paste0(results_dir, "all_results_regional_output_table_2050_pretty.csv"))
```

>>>>

# Now make a min, max, and average for each proposal type
summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>%
  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
  group_by(Category, Year, Variable) %>%
  summarize(Minimum = min(Value, na.rm = T),
            Maximum = max(Value, na.rm = T),
            Median = median(Value, na.rm = T),
            Mean = mean(Value, na.rm = T)) %>%
  arrange(Category)

write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv"))

@@

write.csv(all_results_regional_output_table_2050_pretty, paste0(results_dir, "all_results_regional_output_table_2050_pretty.csv"))

# Now make a min, max, and average for each proposal type
summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>%
  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
  group_by(Region, Category, Year, Variable) %>%
  summarize(Minimum = min(Value, na.rm = T),
            Maximum = max(Value, na.rm = T),
            Median = median(Value, na.rm = T),
            Mean = mean(Value, na.rm = T)) %>%
  arrange(Region, Category)

write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv"))
```
